Material Methods

### 2020-04-17 doc/MatMeth.Rmd
adding in more citations

Meiocyte spreads were incubated with antibody protocol /  Immunohistochemistry was based on that in Anderson et al. (1999) and Koehler et al. (2002).

@@

Each slide was blocked for 30 minutes in ADB incubating with sixty ul of primary antibody master mix (60ul) 
was in ADB and incubated for 48 hours at 37 degrees. The master mix was made (with a primary with polyclonal anti rabbit anti-MLH1 (Calbiochem; diluted 1:50) or anti rabbit anti-DMC1) -- (**mix of DMC1**), anti goat polyclonal antibody to SYCP3, (Abcam; diluted 1:50), and anti-human polyclonal antibody to CREST (Antibodies, Inc; diluted 1:200)

Slides were washed twice in 50ml ADB between primary and secondary antibody incubations.

secondary antibodies master mix was made -- Slides were incubated overnight at 37 degrees in Alexa Fluor 488 donkey anti-rabbit IgG (Invitrgoen, location; diluted to 1:100) and Coumarin AMCA donkey anti-human IgG (Jackson ImmunoResearch; diluted to 1:200).

Alexa Fluor 568 donkey anti-goat (Invitrogen; diluted 1:100) was incubated at 1:100 for 2 hours at 37 degrees. Slides were washed in 1x PBS, dried, and fixed with Prolong Gold Antifade (Invitrogen) for at least 24 hours. Mice with at least 10 cells with good staining were included in our analysis.

@@

Images of cells were capture using a Zeiss Axioplan 2 microscope with AxioLab camera and Axio Vision software (Zeiss, Cambridge, UK). Preprocessing, including cropping, noise reduction, and histogram adjustments, was performed using Photoshop (v13.0). Image file names were anonymized before manual scoring of MLH1 or DMC1 foci using photoshop (cite).

@@

#<A subset of strains, *musculus^PWD^*, *musculus^MSM^*, *domesticus^WSB^*, and *domesticus^G^* were quantified for DMC1.  A total of `r length( (DMC1.DF %>% filter(stage == "Z"))$Original.Name)` and `r length( (DMC1.DF %>% filter(stage == "L"))$Original.Name)` of zygotene and leptotene cells were quantified respectively.>
```
<certeria for DMC1 stained cells (single cells) SC morphology used for staging.>

>>>>

Meiocyte spreads were incubated with antibody protocol /  Immunohistochemistry was based on that in [@anderson1999] and [@koehler2002].

@@

Each slide was blocked for 30 minutes in ADB then incubated with  60ul of primary antibody master mix for 48 hours at 37 degrees. For each master mix polyclonal anti rabbit anti-MLH1 (Calbiochem; diluted 1:50) or anti rabbit anti-DMC1) (mix of DMC1), anti goat polyclonal anti-SYCP3, (Abcam; diluted 1:50), and anti-human polyclonal antibody to CREST (Antibodies, Inc; diluted 1:200) were suspended in ADB. 
Slides were washed twice in 50ml ADB before the first round of secondary antibody incubation for 12 hours at 37 degrees.  Alexa Fluor 488 donkey anti-rabbit IgG (Invitrgoen, location; diluted to 1:100) and Coumarin AMCA donkey anti-human IgG (Jackson ImmunoResearch; diluted to 1:200)  were suspended in ADB. 
The last incubation of Alexa Fluor 568 donkey anti-goat (Invitrogen; diluted 1:100) was incubated at 1:100 for 2 hours at 37 degrees. Slides were fixed with Prolong Gold Antifade (Invitrogen) for 24 hours after a final wash in 1x PBS.

@@

Images of cells were capture using a Zeiss Axioplan 2 microscope with AxioLab camera and Axio Vision software (Zeiss, Cambridge, UK). Preprocessing, including cropping, noise reduction, and histogram adjustments, was performed using Photoshop (v13.0). Image file names were anonymized before manual scoring of MLH1 or DMC1 foci using photoshop.

@@

#<A subset of strains, *musculus^PWD^*, *musculus^MSM^*, *domesticus^WSB^*, and *domesticus^G^* were quantified for DMC1.  A total of `r length( (DMC1.DF %>% filter(stage == "Z"))$Original.Name)` and `r length( (DMC1.DF %>% filter(stage == "L"))$Original.Name)` of zygotene and leptotene cells were quantified respectively.>
```

<certeria for DMC1 stained cells (single cells) SC morphology used for staging.>
